### 2021-11-20 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@4dff9e279780e0c0c7206cc3db0fb63c0833faa6 🚀

The initial success of ODE models can be traced back to the larger
program of ontological reductionism, which became the de facto apporoach
model physical sciences after its early success in physics, which, and
by the time ecology was becoming a quantitative science (sometime in the
20th century, depending on who you ask), became the foundation for early
quantitative models in ecology.

@@

\begin{itemize}
\item
  the missing link paper, turn this into optimizing with two different
  SDMs relative abundance and its effect on false negative
  non-independent associations in samples
\item
  simulate species distribution and efficacy of detection given a set of
  observation points where the dist from observation site decays.
  optimize set of repeated sampling locations L for a \emph{known}
  distribution D. address SDM not being the territory
\end{itemize}

@@

\hypertarget{in-progress-results}{%
\subsubsection{In-progress results}\label{in-progress-results}}

@@

As human activity

This chapter proposes an algorithm for optimizing restoration across
space

(corridorplacement/restoration effort) given a raster where each cell
indicates land-cover. The optimization method uses the result of a
simulated process (specifically occupancy dynamics in the landscape) and
uses simulated annealing to estimate the global optimum of the
targetstate (specfically mean-time-to-extinction for the occupancy
dynamics example).

\hypertarget{methods-2}{%
\subsection{Methods}\label{methods-2}}

@@

\begin{itemize}
\item
  TK conceptual figure with interfaces between what I'm writing / have
\item
  contributed to and linked with other libraries
\item
  \texttt{Observatories.jl}, \texttt{Corridors.jl}, \texttt{MCD.jl}
\end{itemize}

@@

@@

@@

>>>>

The initial success of ODE models can be traced back to the larger
program of ontological reductionism, which became the de facto apporoach
model physical sciences after its early success in physics, which, by
the time ecology was becoming a quantitative science (sometime in the
20th century, depending on who you ask), became the foundation for early
quantitative models in ecology.

@@

It begins with a conceptual framework for understanding the difference
in false-negatives in occurrence, co-occurrence, and interactions
(fig.~3). We use a null model of the relative-abundance distribution
(Hubbell 2001) to simulate realized false-negatives as a function of
varying sampling effort.

This also goes on to includes testing some assumptions of the model with
empirical data fig.~\ref{fig:4}. which indicate our neutral model, if
anything, underestimates the probability of false-negatives due to
positive correlations in co-occurrence in two spatially replicated
networks (Thompson \& Townsend 2000; Hadfield \emph{et al.}
2014)---further I'm planning to add the field data from chapter one into
this anlysis once complete.

\begin{figure}
\centering
\includegraphics{./figures/positiveassociations.png}
\caption{f}
\end{figure}

new addition: - simulate species distribution and efficacy of detection
given a set of observation points where the dist from observation site
decays. optimize set of repeated sampling locations L for a \emph{known}
distribution D. address SDM not being the territory

@@

@@

Promoting landscape connectivity is important to mitigate the effects of
land-use change on Earth's biodiversity. However, the practical
realities of conservation mean that there is a limitation on how much we
can modify landscapes in order to do this. So what is the best place to
put a corridor given a constraint on how much surface-area you can
change in a landscape? This is the question this chapter seeks to
answer. Models for proposing corridor locations have been developed, but
are limited in that are not developed around promoting some element of
ecosystem function, but instead by trying to find the path of least
resistance given a resistance surface (Peterman 2018).

This chapter proposes a general algorithm for optimizing corridor
placement based on a measurement of ecosystem functioning derived from
simulations run on a proposed landscape modification. We propose various
landscape modifications which alter the cover of a landscape,
represented as a raster (fig.~6, left). We then compute a new resistance
surface based on the proposed landscape modification, and based on the
values of resistance to dispersal between each location we simulate
spatially-explicit metapopulation dynamics model (Hanski \& Ovaskainen
2000; Ovaskainen \emph{et al.} 2002) to estimate a distribution of time
until extinction for each landscape modification (fig.~6, right).

@@

@@

\leavevmode\hypertarget{ref-Hadfield2014TalTwo}{}%
Hadfield, J.D., Krasnov, B.R., Poulin, R. \& Nakagawa, S. (2014). A Tale
of Two Phylogenies: Comparative Analyses of Ecological Interactions.
\emph{The American Naturalist}, 183, 174--187.

\leavevmode\hypertarget{ref-Hanski2000MetCap}{}%
Hanski, I. \& Ovaskainen, O. (2000). The metapopulation capacity of a
fragmented landscape. \emph{Nature}, 404, 755--758.

\leavevmode\hypertarget{ref-Hubbell2001UniNeu}{}%
Hubbell, S.P. (2001). \emph{The unified neutral theory of biodiversity
and biogeography}. Monographs in population biology. Princeton
University Press, Princeton.

@@

\leavevmode\hypertarget{ref-Ovaskainen2002MetMod}{}%
Ovaskainen, O., Sato, K., Bascompte, J. \& Hanski, I. (2002).
Metapopulation Models for Extinction Threshold in Spatially Correlated
Landscapes. \emph{Journal of Theoretical Biology}, 215, 95--108.

\leavevmode\hypertarget{ref-Ovaskainen2002MetMod}{}%
Ovaskainen, O., Sato, K., Bascompte, J. \& Hanski, I. (2002).
Metapopulation Models for Extinction Threshold in Spatially Correlated
Landscapes. \emph{Journal of Theoretical Biology}, 215, 95--108.

@@

\leavevmode\hypertarget{ref-Peterman2018ResRP}{}%
Peterman, W.E. (2018). ResistanceGA: An R package for the optimization
of resistance surfaces using genetic algorithms. \emph{Methods in
Ecology and Evolution}, 9, 1638--1647.

\leavevmode\hypertarget{ref-Thompson2000ResSol}{}%
Thompson, R.M. \& Townsend, C.R. (2000). Is resolution the solution?:
The effect of taxonomic resolution on the calculated properties of three
stream food webs. \emph{Freshwater Biology}, 44, 413--422.
